### 2017-05-13 paper/evaluation.tex
minor comments on RQ6

This experiment evaluates the impact of making available to the build
system a growing number of CPUs for testing.  For that reason, we used
a more poweful machine. \Fix{...describe machine...}  We focused on
configuration \ForkSeq{}
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
    \caption{\label{fig:scalability}Scalability.}
\end{wrapfigure}
as the goal of this experiment is to evaluate the impact of spawning a
growing number of JVMs, running on different CPUs.  Furthremore, we
selected the subject \subjectScalability{} as it represents the case
of a long-running test suite (see Figure~\ref{tab:speedup}) with test
cases distributed across many test classes (194 test classes for
\subjectScalability{}).  Note that a test class is the smallest unit
that can be used to spawn a test job on a JVM and that we have no
control over which test classes will be assigned to which JVM that the
build system forks.

>>>>

This experiment evaluates the impact of making available to the build
system a growing number of CPUs for testing.  For that reason, we used
a machine with more cores compared to the one described in
Section~\ref{sec:setup}.  We used a \Fix{...describe machine...}  This
experiment uses configuration \ForkSeq{}
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
    \caption{\label{fig:scalability}Scalability.}
\end{wrapfigure}
as the goal is to evaluate the impact on runtime of spawning a growing number of
JVMs in different CPUs.  Furthremore, we selected subject
\subjectScalability{} as it represents the case of a long-running test
suite (see Figure~\ref{tab:speedup}) with test cases distributed
across many test classes (194 test classes for \subjectScalability{}).
Note that a test class is the smallest unit that can be used to spawn
a test job on a JVM and that we have no control over which test
classes will be assigned to which JVM that the build system forks.
